\documentclass{article}
\usepackage{enumitem}
\begin{document}

\title{Questions}
\author{}
\date{}
\maketitle

\begin{enumerate}
    \item What is the disadvantage of asynchronous transmission?
    \item Describe stop-and-wait flow control.
    \item Explain the CRC technique for error detection.
    \item Describe the three HDLC transfer modes.
    \item Briefly explain the Delta Modulation technique.
    \item Define the Nyquist bandwidth.
    \item Define the Shannon capacity formula.
    \item What are the benefits of spread spectrum?
    \item What is multiplexing?
    \item Explain frequency-hopping spread spectrum with proper diagram.
    \item Explain direct sequence spread spectrum with proper diagram.
    \item Discuss the three versions of ARQ with proper diagram.
    \item Explain the working of synchronous time division multiplexing (TDM) with proper diagram.
    \item Explain the working of frequency division multiplexing (FDM) with proper diagram.
    \item Explain the sliding-window flow control with proper diagram.
    \item What is the advantage of sliding-window flow control compared to stop-and-wait flow control?
    \item Find the Bipolar-AMI, Pseudoternary, Manchester, and Differential Manchester encoding for the binary data 100110111.
    \item Explain the difference between datagram and virtual circuit operation.
    \item Discuss the various Congestion control techniques.
    \item Write short notes on:
    \begin{itemize}
        \item X.25
        \item Frame Relay
    \end{itemize}
    \item Write short notes on:
    \begin{itemize}
        \item Internet Control Message Protocol (ICMP)
        \item IPV6
    \end{itemize}
    \item Write short notes on:
    \begin{itemize}
        \item Internet Group Management Protocol (IGMP)
        \item Open Shortest Path First (OSPF)
    \end{itemize}
\end{enumerate}

\end{document}
